### 2025-02-20 introduction.tex
new

Successful risk management practice can ensure the stability and resilience against a variety of risks.

@@

It provides a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.

@@

Two interesting problems that requires nested simulation are considered in this thesis:  

@@

We argue that for estimating tail risk measures of VA contact losses, the inner simulation can be replaced entirely by a suitable metamodel. 

@@

One of the primary risk management strategies employed by insurers to mitigate the financial risks associated with VAs is dynamic hedging. 
Dynamic hedging involves a frequent adjustment of a portfolio of financial instruments to offset changes in the value of the guarantees due to market movements~\citep{hull2016options}. 
This strategy aims at neutralizing the sensitivity of the insurer's liability to market fluctuations by constructing a hedging portfolio that replicates the cash flows of the guarantees.
However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure.
One such example is the estimation of tail risk measures of a VA contract.
It requires the stochastic modeling of the financial market and the accurate loss estimation of the hedging portfolio under different market scenarios.
Nested simulation has emerged as a robust method for estimating risk measures in such complex settings~\citep{gordy2010nested}.
In nested simulation, an outer simulation generates a set of market scenarios over the contract horizon, while an inner simulation estimates the contract loss in each scenario.
By combining the results of the inner simulations across the outer scenarios, nested simulation provides an accurate estimate of the tail risk of the VA contract.

@@

Metamodeling, also known as surrogate modeling, is a technique used to approximate complex simulation models with simpler, computationally efficient models. 
In the context of Monte Carlo simulations, metamodels are models of models that aim at reducing computational costs by creating an approximate model that can quickly predict simulation outputs based on input variables~\citep{kleijnen2018design}. 
This section introduces metamodeling for a Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.

Monte Carlo simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature. 
These simulations often require a substantial amount of computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}. 
Metamodeling addresses this challenge by constructing an approximate model (known as ametamodel) that emulates the behavior of the original simulation model with much less computational effort.
The metamodel serves as a predictive model that maps input variables to output responses. 
Learning from a set of simulation runs, the metamodel can generalize and predict outputs for new inputs without running the full simulation.
Metamodeling is particularly useful when the simulation model is computationally expensive. 
By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be substantially reduced. 
This allows for faster convergence of simulation-based estimators.

@@

The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
Example use cases for machine learning include~\cite{jin2020deep}, ~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might have to struggle to model them effectively.
In the following sections, we discuss machine learning algorithms in the context of metamodeling for Monte Carlo simulations and their applications in risk management.

@@

Supervised learning is a fundamental approach in machine learning where the algorithm learns a mapping from inputs to outputs based on example input-output pairs \cite{galton1886regression}. 
In this paradigm, a model is trained on a labeled dataset, which means that each training example is associated with an output label or value. 
The goal of a supervised learning paradigm is to learn a general rule that maps inputs (also known as features) to outputs (also known as target), enabling the model to make accurate predictions on new, unseen data.
Supervised learning can be carried out in two domains of applications.
These are:

\begin{itemize} 
    \item \textbf{Classification}: The output variable is categorical, and the task is to assign inputs to one of several predefined categories to produce a qualitative prediction. 
    Common use in finance and actuarial applications are fraud detection and credit scoring.
    \item \textbf{Regression}: The output variable is continuous, and the task is to predict a real-valued number and produce a quantitative prediction. 
    Examples in actuarial applications include predicting claim amounts, reserve estimates, asset pricing, and estimating tail risk measures of loss distributions.
\end{itemize}

This thesis focuses on regression models for risk management applications, where the goal is to predict a continuous target variable based on one or more input features.
Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learning a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input vector of features $x$ with a vector of function parameters $\theta$.

@@

In most risk management applications, a critical task of users of supervised learning models is to design a suitable loss function that aligns with the objectives of the problem.
Another important consideration is the choice of a suitable supervised learning algorithm.
The choice may vary based on a trade-off among the complexity of the relationship, the interpretability of the model, and the computational resources available.
In the following sections, we discuss four widely used supervised learning techniques in risk management applications: parametric regression, kernel regression, and two neural network architectures.

@@

Regression models are the most common supervised learning algorithms used in risk management applications.
A regression model predicts a continuous target variable based on one or more input features.
A multiple linear regression is a simple and interpretable model that attempts to predict a target variable as a linear combination of input features. 
It assumes a linear relationship between the target output and one or more input features. 
This method has been thoroughly explored in statistical literature. 
\citet{bishop2006pattern} provide an extensive treatment of regression techniques in the broader context of machine learning.
It is known as a parametric regression because it assumes a specific functional form for the input-output relationship with a finite set of parameters~\citep{seber2012linear}.
A general form of a parametric regression model is given by:
\begin{equation} \label{eq:regression}
    f(x; \theta) = \beta_0 + \sum_{j=1}^{p} \beta_j \phi_j(x),
\end{equation}
where $p$ is a number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are trainable regression coefficients, and $\phi_j(x)$ are basis functions that transfrom the input $x$ to allow for non-linear modeling.
Basis functions can be any functions of $x$ that are chosen to capture the underlying structure of the data.
Common choices include polynomial basis functions: $\phi_j(x) = x^j$ and Laguerre basis functions: $\phi_j(x) = e^{-x/2} L_j(x)$, where $L_j(x)$ are the Laguerre polynomials that are solutions to the Laguerre differential equation~\citep{szeg1939orthogonal}.
The training of parametric regression refers to the process of estimating the regression coefficients $\beta_0, \beta_1, \ldots, \beta_p$ that minimize the loss function.
For a MSE loss metrics, the optimal regression coefficients can be obtained by solving the normal equations.
Parametric regression is a powerful tool for modeling linear relationships where the basis functions are known from expert knowledge for explicit feature engineering techniques~\citep{hastie2009elements}.
These techniques utilize predefined functional forms to model the relationship between a set of independent variables and a dependent variable. 
However, when data exhibits complex, non-linear relationships, linear models fall short. 
While these methods are straightforward and interpretable, they impose strong assumptions about the underlying data structure.
Often, expert knowledge is required to select the appropriate basis functions, which can limit the flexibility of the model.
Extensions like polynomial regression and generalized linear models (GLMs) have been introduced to capture non-linearity in the data.
Nevertheless, these models can still be limited in capturing highly complex patterns of the data.

\subsection{Non-Parametric Regression Models}
To overcome some of the previously mentioned limitations of the parametric regression, non-parametric methods such as kernel regression~\citep{hastie2009elements} are often employed. 
Kernel regression estimates the relationship by averaging the values of the target variable over a local neighborhood of the input $x$.
The kernel regression with the Nadaraya-Watson estimator is given by:
\begin{equation}
    f(x; \theta) = \frac{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right) y_i}{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right)},
\end{equation}
where $K(\cdot)$ is a kernel function, which assigns weights to the data points based on their distance to the input $x$, and $h$ is a bandwidth parameter that controls the smoothness of the estimated function.
The objective of this approach is to estimate a feature-label relationship directly from the data without imposing a specific functional form of the regression function.
However, they come with several drawbacks that limit their effectiveness, especially in high-dimensional settings or for large datasets. 
One of the most important drawbacks of the non-parametric regression is the curse of dimensionality \cite{bellman1966dynamic}. 
As the number of features increases, the volume of the input space grows exponentially.
Data points become sparse and the model may overfit to noise in the data.
In addition, the computational cost associated with non-parametric methods often grows rapidly with the number of dimensions.
Cross validation and distance calculation are two computationally expensive operations that are often required for a non-parametric regression.
These drawbacks make the non-parametric regression impractical for modeling high-dimensional large-scale datasets.

@@

The progression from traditional parametric and non-parametric regression methods to neural network architectures has been driven by the need to model increasingly complex and high-dimensional data.
Neural networks have emerged as powerful tools capable of overcoming many limitations of traditional regression methods. 
They can learn complex, non-linear relationships in data without the need for explicit feature engineering.
The most crude form of a neural network is the feedforward neural network (FNN), which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.

@@

\begin{equation}
    f(x; \theta) = f^{(k)}(f^{(k-1)} \cdots (f^{(2)}(f^{(1)}(x;\theta^{(1)});\theta^{(2)} )\cdots ;\theta^{(k-1)});\theta^{(k)}),
\end{equation}
where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are trainable parameters of the neural network, $f^{(i)}$ is an $i$-th layer of the neural network, $x$ is an input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is an output layer, $k$ is a number of layers, and $f^{(i)}$ is an output of the $i$-th layer.
To move from a lower layer to a higher layer, i.e., from layer $i-1$ to layer $i$,

\begin{equation} \label{eq:neural}
    f^{(i)}(z;\theta^{(i)}) = a^{(i)}(\beta_0^{(i)} + \sum_{j=1}^{p_i} \beta_j^{(i)} z),
\end{equation}
where $a^{(i)}$ are nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are trainable parameters of the $i$-th layer, and $p_i$ is a number of neurons in the previous layer.
Equation~\ref{eq:neural} represents a single neuron in a neural network, which applies a linear transformation to the input followed by a non-linear activation function. 
The linear transformation is similar to the linear regression model in Equation~\ref{eq:regression}, but the non-linear activation function allows the neural network to model complex, non-linear relationships in the data.
The FNN is tuned by adjusting the trainable parameters $\theta$ while fixing the activation functions $a^{(i)}$.
A typical choice for the activation function is the rectified linear unit (ReLU), which is defined as $a(z) = \max(0, z)$~\citep{nair2010rectified}.
The choice of an activation function also plays a crucial role in the training of neural networks.
While sigmoid and hyperbolic tangent functions were popular in early neural networks, ReLU has become the default activation function for deep networks due to its ability to mitigate the vanishing gradient problem and promote sparse activations~\citep{lecun2015deep}.

The key advantage of FNNs lies in their ability to perform automatic feature engineering without a direct human intervention. 
Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during the training. 
Each hidden layer in the network captures higher-level abstractions of the input data by transforming the outputs of the previous layer through nonlinear activation functions~\citep{lecun2015deep}.
Each layer builds upon the representations learned by the previous layer, enabling the network to capture multiple levels of abstraction. 
This characteristic is crucial for modeling complex datasets with intricate patterns and relationships~\citep{bengio2013representation}.

The last layer of the neural network, known as the output layer, typically performs a linear transformation of the features extracted by the preceding hidden layers. 
With $a^{k}(z) = z$, the last layer is equivalent to a multiple linear regression with its inputs as transformed, high-level features learned by the hidden layers.
We can draw parallels between neural networks and traditional regression models. 
The main difference is that, in neural networks, the input features to the regression model are learned automatically rather than being manually specified.

@@

To overcome the limitations of FNNs in handling sequential input, recurrent neural networks (RNNs) were introduced.
In a RNN, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:

@@

To address these issues, a long short-term memory (LSTM) network was developed by \citet{hochreiter1997long}.
It is a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of RNN memory cells and gating mechanisms.

@@

The advancements in neural network optimization techniques, architectures, and training methodologies have significantly enhanced their usefulness in risk management applications.
By effectively modeling complex, non-linear relationships and temporal dependencies, neural networks serve as powerful tools for addressing the computational challenges in estimating risk measures and developing effective risk mitigation strategies.
This thesis aims at exploring the application and noise tolerance of LSTM networks in metamodeling for nested simulation procedures in risk management.
In this thesis, we investigate the performance of LSTM networks in approximating the inner simulation model in a two-stage nested simulation procedure for index-linked insurance contracts.
By leveraging the memory and sequential modeling capabilities of LSTMs, we aim to improve the accuracy and efficiency of nested simulation procedures for risk management applications.

@@

The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function, which quantifies the error between the predictions and the labels.
The training process aims at finding the optimal parameters that minimize this error.
The most common approach is to use gradient descent methods with backpropagation, which is an efficient method for computing the gradients of the loss function with respect to the trainable parameters.
Backpropagation computes the gradients by propagating the error derivatives backward through the network layers.
This process allows the network to adjust the parameters in the direction of minimizing the loss function.
The training process is typically performed over a number of epochs, where each epoch is one complete pass through the training dataset.

However, the training of neural networks is non-convex, and the optimization problem is challenging.
Stochastic gradient descent (SGD) is a popular optimization algorithm for training neural networks.
It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than the crude gradient descent.
However, SGD may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
To address these issues, various adaptive learning rate methods have been proposed in the literature.
The most popular approach is Adam optimizer, which is a SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.

Another common technique to improve the training of neural networks is a regularization technique to prevent overfitting.
One effective regularization method is dropout, which randomly sets a fraction of neurons to zero during each training iteration~\citep{srivastava2014dropout}.
This prevents neurons from co-adapting too much, encourages redundancy, and leads to a more robust model that generalizes better to unseen data.
Early stopping is another regularization method that is relevant to our study.
It involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
This helps prevent over-fitting by stopping training before the model begins to fit to the noise in the data.

Evaluation of the performance of a neural network is challenging due to the absence of analytical tools.
Existing machine learning literature addresses this challenge by splitting the data into three parts: training set, validation set, and test set.
The training set is used to train the model, the validation set is used to tune the model hyper-parameters, and the test set is used to evaluate how well the model generalizes to unseen data.
The test set is not used during training and is only used for an evaluation purpose.

Under-fitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
Over-fitting occurs when the neural network fits to the noise in the training data and cannot generalize results to unseen data.
In machine learning literature, over-fitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
During training, as the test dataset is not used, this quantity is estimated by using the validation set.
If the validation error is high compared to the training error, the model is likely over-fitting to the training data.

In practice, the ultimate performance of a neural network is often evalutated based on error metrics on the test dataset and how it compares with the training error. 
The test error is often thought to be a reliable indicator of the model's generalization capability for most machine learning applications.
However, real-world datasets often contain noise.
As the test dataset is separated from the training dataset, it is often contaminated with noise.
Therefore, the test error may not be robust for evaluating the generalization capability of a neural network.
In this thesis, we aim to evaluate the generalization capability of neural networks in a simulation environment.
For a simulation model, we can generate a large number of datasets with different levels of noise.
The noise level can be controlled by the design parameters of the simulation model, e.g., the number of replications.
Instead of relying on the noisy test labels, we can generate a less noisy test labels using a higher number of replications, or even the true simulation model.
In the rest of this thesis, we will use ``test dataset'' or ``test labels'' to refer to the noisy test dataset, and ``true dataset'', ``true labels'', or ``true relationship'' to refer to dataset generated from the true simulation model.

>>>>

Successful risk management practice can ensure stability and resilience against a variety of risks.

@@

They provide a guaranteed minimum income benefit to the policyholder regardless of the performance of the underlying assets.

@@

Two interesting problems that require nested simulation are considered in this thesis:  

@@

We argue that for estimating tail risk measures of VA contract losses, the inner simulation can be replaced entirely by a suitable metamodel. 

@@

One of the primary risk management strategies employed by insurers to mitigate the financial risks associated with VAs is dynamic hedging. 
Dynamic hedging involves a frequent adjustment of a portfolio of financial instruments to offset changes in the value of the guarantees due to market movements~\citep{hull2016options}. 
This strategy aims to neutralize the sensitivity of the insurer's liability to market fluctuations by constructing a hedging portfolio that replicates the cash flows of the guarantees.
However, dynamic hedging introduces complexity in estimating the insurer's overall risk exposure.
One such example is the estimation of tail risk measures of a VA contract.
It requires a stochastic modeling of the financial market and an accurate loss estimation of the hedging portfolio under different market scenarios.
Nested simulation has emerged as a robust method for estimating risk measures in such complex settings~\citep{gordy2010nested}.
In nested simulation, an outer simulation generates a set of market scenarios over the contract horizon, while an inner simulation estimates the contract loss in each scenario.
By combining the results of the inner simulations across the outer scenarios, nested simulation provides an accurate estimate of the tail risk of the VA contract.

@@

Metamodeling, also known as surrogate modeling, is a technique used to approximate complex simulation models with simpler, computationally efficient models. 
In the context of Monte Carlo simulations, metamodels are models of models that aim to reduce computational costs by creating an approximate model that can quickly predict simulation outputs based on input variables~\citep{kleijnen2018design}. 
This section introduces metamodeling for Monte Carlo simulation, elaborates on its methodologies, and highlights its importance in practical applications.

Monte Carlo simulations are widely used for modeling and analyzing complex systems that are probabilistic in nature. 
These simulations often require substantial computational resources, especially when a high degree of accuracy or a high number of iterations is necessary~\citep{glasserman2004monte}. 
Metamodeling addresses this challenge by constructing an approximate model (known as a metamodel) that emulates the behavior of the original simulation model with much less computational effort.
The metamodel serves as a predictive model that maps input variables to output responses. 
Learning from a set of simulation runs, the metamodel can generalize and predict outputs for new inputs without running the full simulation.
Metamodeling is particularly useful when the simulation model is computationally expensive. 
By replacing the simulation model with a metamodel, the computational cost of evaluating the model can be substantially reduced. 
This allows for faster convergence of simulation-based estimators.

@@

The development of advanced machine learning models and deep learning techniques has enhanced metamodeling approaches for Monte Carlo simulations, especially in high-dimensional and complex problem settings.
Example use cases for machine learning include~\cite{jin2020deep}, ~\cite{tang2020deep}, and~\cite{rosen2012metamodeling}.
These methods offer powerful tools for capturing intricate patterns and nonlinear relationships that traditional metamodeling techniques might struggle to model effectively.
In the following sections, we discuss machine learning algorithms in the context of metamodeling for Monte Carlo simulations and their applications in risk management.

@@

Supervised learning is a fundamental approach in machine learning where the algorithm learns a mapping from inputs to outputs based on example input-output pairs \cite{galton1886regression}. 
In this paradigm, a model is trained on a labeled dataset, which means that each training example is associated with an output label or value. 
The goal of a supervised learning paradigm is to learn a general rule that maps inputs (also known as features) to outputs (also known as targets), enabling the model to make accurate predictions on new, unseen data.
Supervised learning can be carried out in two domains of applications.
These are:

\begin{itemize} 
    \item \textbf{Classification}: The output variable is categorical, and the task is to assign inputs to one of several predefined categories to produce a qualitative prediction. 
    Common uses in finance and actuarial applications are fraud detection and credit scoring.
    \item \textbf{Regression}: The output variable is continuous, and the task is to predict a real-valued number and produce a quantitative prediction. 
    Examples in actuarial applications include predicting claim amounts, reserve estimates, asset pricing, and estimating tail risk measures of loss distributions.
\end{itemize}

This thesis focuses on regression models for risk management applications, where the goal is to predict a continuous target variable based on one or more input features.
Given a dataset of $n$ observations $\{(x_1, y_1), (x_2, y_2), \ldots, (x_n, y_n)\}$, where $x_i \in \mathbb{R}^d$ is the $d$-dimensional input feature vector, and $y_i \in \mathbb{R}$ is the target variable, a supervised learning algorithm aims to learn a function $f(;\theta): \mathbb{R}^d \rightarrow \mathbb{R}$ that best predicts the target variable $y$ given the input vector of features $x$ with a vector of function parameters $\theta$.

@@

In most risk management applications, a critical task for users of supervised learning models is to design a suitable loss function that aligns with the objectives of the problem.
Another important consideration is the choice of a suitable supervised learning algorithm.
The choice may vary based on a trade-off among the complexity of the relationship, the interpretability of the model, and the computational resources available.
In the following sections, we discuss four widely used supervised learning techniques in risk management applications: parametric regression, kernel regression, and two neural network architectures.

@@

Regression models are the most common supervised learning algorithms used in risk management applications.
A regression model predicts a continuous target variable based on one or more input features.
Multiple linear regression is a simple and interpretable model that attempts to predict a target variable as a linear combination of input features. 
It assumes a linear relationship between the target output and one or more input features. 
This method has been thoroughly explored in statistical literature. 
\citet{bishop2006pattern} provides an extensive treatment of regression techniques in the broader context of machine learning.
It is known as parametric regression because it assumes a specific functional form for the input-output relationship with a finite set of parameters~\citep{seber2012linear}.
A general form of a parametric regression model is given by:
\begin{equation} \label{eq:regression}
    f(x; \theta) = \beta_0 + \sum_{j=1}^{p} \beta_j \phi_j(x),
\end{equation}
where $p$ is the number of features, $\beta_0, \beta_1, \ldots, \beta_p$ are trainable regression coefficients, and $\phi_j(x)$ are basis functions that transform the input $x$ to allow for non-linear modeling.
Basis functions can be any functions of $x$ that are chosen to capture the underlying structure of the data.
Common choices include polynomial basis functions: $\phi_j(x) = x^j$ and Laguerre basis functions: $\phi_j(x) = e^{-x/2} L_j(x)$, where $L_j(x)$ are the Laguerre polynomials that are solutions to the Laguerre differential equation~\citep{szeg1939orthogonal}.
The training of parametric regression refers to the process of estimating the regression coefficients $\beta_0, \beta_1, \ldots, \beta_p$ that minimize the loss function.
For an MSE loss metric, the optimal regression coefficients can be obtained by solving the normal equations.
Parametric regression is a powerful tool for modeling linear relationships where the basis functions are known from expert knowledge or explicit feature engineering techniques~\citep{hastie2009elements}.
These techniques utilize predefined functional forms to model the relationship between a set of independent variables and a dependent variable. 
However, when data exhibits complex, non-linear relationships, linear models fall short. 
While these methods are straightforward and interpretable, they impose strong assumptions about the underlying data structure.
Often, expert knowledge is required to select the appropriate basis functions, which can limit the flexibility of the model.
Extensions like polynomial regression and generalized linear models (GLMs) have been introduced to capture non-linearity in the data.
Nevertheless, these models can still be limited in capturing highly complex patterns in the data.

\subsection{Non-Parametric Regression Models}
To overcome some of the previously mentioned limitations of parametric regression, non-parametric methods such as kernel regression~\citep{hastie2009elements} are often employed. 
Kernel regression estimates the relationship by averaging the values of the target variable over a local neighborhood of the input $x$.
The kernel regression with the Nadaraya-Watson estimator is given by:
\begin{equation}
    f(x; \theta) = \frac{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right) y_i}{\sum_{i=1}^{n} K\left(\frac{x-x_i}{h}\right)},
\end{equation}
where $K(\cdot)$ is a kernel function, which assigns weights to the data points based on their distance to the input $x$, and $h$ is a bandwidth parameter that controls the smoothness of the estimated function.
The objective of this approach is to estimate a feature-label relationship directly from the data without imposing a specific functional form of the regression function.
However, they come with several drawbacks that limit their effectiveness, especially in high-dimensional settings or for large datasets. 
One of the most important drawbacks of non-parametric regression is the curse of dimensionality \cite{bellman1966dynamic}. 
As the number of features increases, the volume of the input space grows exponentially.
Data points become sparse and the model may overfit to noise in the data.
In addition, the computational cost associated with non-parametric methods often grows rapidly with the number of dimensions.
Cross validation and distance calculation are two computationally expensive operations that are often required for non-parametric regression.
These drawbacks make non-parametric regression impractical for modeling high-dimensional large-scale datasets.

@@

The progression from traditional parametric and non-parametric regression methods to neural network architectures has been driven by the need to model increasingly complex and high-dimensional data.
Neural networks have emerged as powerful tools capable of overcoming many limitations of traditional regression methods. 
They can learn complex, non-linear relationships in data without the need for explicit feature engineering.
The most basic form of a neural network is the feedforward neural network (FNN), which consists of an input layer, one or more hidden layers, and an output layer~\citep{goodfellow2016}.

@@

\begin{equation}
    f(x; \theta) = f^{(k)}(f^{(k-1)} \cdots (f^{(2)}(f^{(1)}(x;\theta^{(1)});\theta^{(2)} )\cdots ;\theta^{(k-1)});\theta^{(k)}),
\end{equation}
where $\theta = (\theta^{(1)}, \theta^{(2)}, \ldots, \theta^{(k)})$ are trainable parameters of the neural network, $f^{(i)}$ is the $i$-th layer of the neural network, $x$ is an input feature vector, $f^{(1)}(x;\theta^{(1)}) = x$, $f^{(k)}$ is an output layer, $k$ is the number of layers, and $f^{(i)}$ is an output of the $i$-th layer.
To move from a lower layer to a higher layer, i.e., from layer $i-1$ to layer $i$,

\begin{equation} \label{eq:neural}
    f^{(i)}(z;\theta^{(i)}) = a^{(i)}(\beta_0^{(i)} + \sum_{j=1}^{p_i} \beta_j^{(i)} z),
\end{equation}
where $a^{(i)}$ are nonlinear activation functions, $\theta^{(i)} = (\beta_0^{(i)}, \dots, \beta_p^{(i)})$ are trainable parameters of the $i$-th layer, and $p_i$ is the number of neurons in the previous layer.
Equation~\ref{eq:neural} represents a single neuron in a neural network, which applies a linear transformation to the input followed by a non-linear activation function. 
The linear transformation is similar to the linear regression model in Equation~\ref{eq:regression}, but the non-linear activation function allows the neural network to model complex, non-linear relationships in the data.
The FNN is tuned by adjusting the trainable parameters $\theta$ while fixing the activation functions $a^{(i)}$.
A typical choice for the activation function is the rectified linear unit (ReLU), which is defined as $a(z) = \max(0, z)$~\citep{nair2010rectified}.
The choice of an activation function also plays a crucial role in the training of neural networks.
While sigmoid and hyperbolic tangent functions were popular in early neural networks, ReLU has become the default activation function for deep networks due to its ability to mitigate the vanishing gradient problem and promote sparse activations~\citep{lecun2015deep}.

The key advantage of FNNs lies in their ability to perform automatic feature engineering without direct human intervention. 
Unlike traditional machine learning models that require manual selection and transformation of input features, neural networks learn to extract and compose features through their hidden layers during training. 
Each hidden layer in the network captures higher-level abstractions of the input data by transforming the outputs of the previous layer through nonlinear activation functions~\citep{lecun2015deep}.
Each layer builds upon the representations learned by the previous layer, enabling the network to capture multiple levels of abstraction. 
This characteristic is crucial for modeling complex datasets with intricate patterns and relationships~\citep{bengio2013representation}.

The last layer of the neural network, known as the output layer, typically performs a linear transformation of the features extracted by the preceding hidden layers. 
With $a^{k}(z) = z$, the last layer is equivalent to multiple linear regression with its inputs as transformed, high-level features learned by the hidden layers.
We can draw parallels between neural networks and traditional regression models. 
The main difference is that, in neural networks, the input features to the regression model are learned automatically rather than being manually specified.

@@

To overcome the limitations of FNNs in handling sequential input, recurrent neural networks (RNNs) were introduced.
In an RNN, the hidden state at each time step is a function of both the current input and the hidden state from the previous time period~\citep{elman1990finding}:

@@

To address these issues, long short-term memory (LSTM) networks were developed by \citet{hochreiter1997long}.
They are a specialized form of RNNs designed to capture long-term dependencies more effectively with the help of RNN memory cells and gating mechanisms.

@@

The advancements in neural network optimization techniques, architectures, and training methodologies have significantly enhanced their usefulness in risk management applications.
By effectively modeling complex, non-linear relationships and temporal dependencies, neural networks serve as powerful tools for addressing the computational challenges in estimating risk measures and developing effective risk mitigation strategies.
This thesis aims to explore the application and noise tolerance of LSTM networks in metamodeling for nested simulation procedures in risk management.
In this thesis, we investigate the performance of LSTM networks in approximating the inner simulation model in a two-stage nested simulation procedure for index-linked insurance contracts.
By leveraging the memory and sequential modeling capabilities of LSTMs, we aim to improve the accuracy and efficiency of nested simulation procedures for risk management applications.

@@

The training of neural networks involves adjusting the trainable parameters of the network to minimize the loss function, which quantifies the error between the predictions and the labels.
The training process aims to find the optimal parameters that minimize this error.
The most common approach is to use gradient descent methods with backpropagation, which is an efficient method for computing the gradients of the loss function with respect to the trainable parameters.
Backpropagation computes the gradients by propagating the error derivatives backward through the network layers.
This process allows the network to adjust the parameters in the direction of minimizing the loss function.
The training process is typically performed over a number of epochs, where each epoch is one complete pass through the training dataset.

However, the training of neural networks is non-convex, and the optimization problem is challenging.
Stochastic gradient descent (SGD) is a popular optimization algorithm for training neural networks.
It updates the parameters using a single or a small batch of training examples at a time, which makes it much faster than crude gradient descent.
However, SGD may oscillate and converge slowly, especially in non-convex problems~\citep{bengio2016}.
To address these issues, various adaptive learning rate methods have been proposed in the literature.
The most popular approach is the Adam optimizer, which is an SGD algorithm that adjusts the learning rate during training to improve convergence speed and stability~\citep{kingma2014adam}.

Another common technique to improve the training of neural networks is regularization to prevent overfitting.
One effective regularization method is dropout, which randomly sets a fraction of neurons to zero during each training iteration~\citep{srivastava2014dropout}.
This prevents neurons from co-adapting too much, encourages redundancy, and leads to a more robust model that generalizes better to unseen data.
Early stopping is another regularization method that is relevant to our study.
It involves monitoring the model's performance on a validation set and stopping training when the performance no longer improves~\citep{prechelt2002early}.
This helps prevent overfitting by stopping training before the model begins to fit to the noise in the data.

Evaluation of the performance of a neural network is challenging due to the absence of analytical tools.
Existing machine learning literature addresses this challenge by splitting the data into three parts: training set, validation set, and test set.
The training set is used to train the model, the validation set is used to tune the model hyperparameters, and the test set is used to evaluate how well the model generalizes to unseen data.
The test set is not used during training and is only used for evaluation purposes.

Underfitting occurs when the training error is high, which means that the neural network fails to capture the underlying patterns in the training data.
Overfitting occurs when the neural network fits to the noise in the training data and cannot generalize results to unseen data.
In machine learning literature, overfitting is often quantified as the gap between the training error and the test error~\citep{bishop2006pattern}.
During training, as the test dataset is not used, this quantity is estimated by using the validation set.
If the validation error is high compared to the training error, the model is likely overfitting to the training data.

In practice, the ultimate performance of a neural network is often evaluated based on error metrics on the test dataset and how it compares with the training error. 
In practice, the ultimate performance of a neural network is often evalutated based on error metrics on the test dataset and how it compares with the training error. 
The test error is often thought to be a reliable indicator of the model's generalization capability for most machine learning applications.
However, real-world datasets often contain noise.
As the test dataset is separated from the training dataset, it is often contaminated with noise.
Therefore, the test error may not be robust for evaluating the generalization capability of a neural network.
In this thesis, we aim to evaluate the generalization capability of neural networks in a simulation environment.
For a simulation model, we can generate a large number of datasets with different levels of noise.
The noise level can be controlled by the design parameters of the simulation model, e.g., the number of replications.
Instead of relying on the noisy test labels, we can generate a less noisy test labels using a higher number of replications, or even the true simulation model.
In the rest of this thesis, we will use ``test dataset'' or ``test labels'' to refer to the noisy test dataset, and ``true dataset'', ``true labels'', or ``true relationship'' to refer to dataset generated from the true simulation model.
